Carbonate chemistry at Ny-Ålesund

### 2021-11-23 awipev-CO2.Rmd
on going work on pH seafet

# we look at all depths
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf, depth) %>%
  group_by(depth, montht)
p <- tmp %>% 
  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
  facet_wrap(vars(montht), scale = "free_y")
print(p)

# we look at 0 to 4 m vs more than 8 m
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf, depth) %>%
  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
  dplyr::filter(depth == 2 | depth == 10) %>% 
  group_by(depth, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))

>>>>

# tmp <- d_all %>% 
#   dplyr::select(montht, pHint_tot_sf, depth, depth_discrete) %>%
#   dplyr::group_by(depth, montht)
# p <- tmp %>% 
#   ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
#   facet_wrap(vars(montht), scale = "free_y")
# print(p)
# 
# 
# p <- tmp %>% 
#   ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
#   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
#   facet_wrap(vars(montht), scale = "free_y")
# print(p)

# we look at all depths
tmp <- d_all %>% 
  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
  dplyr::group_by(depth_discrete, year, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))

# remove outliers
quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))

p <- tmp %>%
  ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, coef = 1.5) +
  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
  lims(y = c(7.4, 8.3)) +
  coord_cartesian() +
  facet_wrap(vars(montht), scale = "fixed")
print(p)

pp <- tmp %>%
  ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
  stat_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, coef = 3)

# we look at 0 to 4 m vs more than 8 m
tmp <- d_all %>% 
  dplyr::select(montht, pHint_tot_sf, depth) %>%
  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
  dplyr::filter(depth == 2 | depth == 10) %>% 
  dplyr::group_by(depth, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))
